Ecuador Elevation

### 2022-10-21 code/L0/L0_Ecuador_elevation.Rmd
get elevation data using elevatr package

---
title: "Ecuador Elevation"
author: "Hazel J. Anderson"
collaborators: "None"
data input: "None"
data output: "TBD"
project: "Frugivoria"
date: "2022-10-10"
output: html_document
---

@@

# Download elevation data for Ecuador using geodata
```{r}
# get outline of Ecuador
ecuador_outline <- gadm(country = "ECU", level=1, path = data_path, version="latest", resolution=1)
ecuador_outline

@@

# look at elevation data
plot(ecuador_geodata)

@@

# Download elevation data for Ecuador using 'elevatr'
```{r}
#NEED TO CONVERT ecuador_outline to spatial dataframe
ecuador_outline.df <- as.data.frame(ecuador_outline)
ecuador_elevatr <- get_elev_raster(ecuador_outline.df, z= 5)
```

>>>>

---
title: "Ecuador Elevation"
author: "Hazel J. Anderson"
collaborators: "None"
data input: "None"
data output: "ecuador_geodata_elevation.RData and ecuador_elevatr_elevation.RData"
project: "Frugivoria"
date: "2022-10-21"
output: html_document
---

@@

# Download elevation data for Ecuador using geodata
```{r}
# get outline of Ecuador
ecuador_outline <- gadm(country = "ECU", level=0, path = data_path, version="latest", resolution=1)
ecuador_outline

@@

# look at elevation data
plot(ecuador_geodata)
plot(ecuador_outline, add = T)

@@

# Download elevation data for Ecuador using 'elevatr'
```{r}
# convert ecuador_outline to spatial dataframe
ecuador_outline.df <- sf::st_as_sf(ecuador_outline)

# get elevation data for Ecuador
ecuador_elevatr <- get_elev_raster(ecuador_outline.df, z= 5)

# plot elevation
plot(ecuador_elevatr)
plot(ecuador_outline, add = T)

#save elevation data to file
ecuador_elevatr_elevation_path <- file.path(output_path,"ecuador_elevatr_elevation.RData") 
save(ecuador_elevatr, file = ecuador_elevatr_elevation_path)
```
